ACNP 2024 MS ANXIETY

### 2024-07-26 scripts/ACNP2024_MSAnxiety.Rmd
fixed indiv fascicle analyses

    anxietyGrouping_mean_UF_by_sex_gam <- gam(mean_UF_vol ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = F), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
  summary(anxietyGrouping_mean_UF_by_sex_gam)
```

@@

@@

### 3 meet FDR - C_FPH_R_prop	0.037			C_FP_R_prop	0.042			DRTT_R_prop	0.042
df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
  filter(anxiety_dose != 3) %>%
  mutate(anxiety_dose_factor = ordered(anxiety_dose))

#lm
fascicle_lm <- lapply(fascicle_names_w_prop_suffix, function(x) 
{
  lm(substitute(i ~ oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed + PAT_AGE_AT_EXAM, list(i = as.name(x))), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
})
names(fascicle_lm) <- fascicle_names_w_prop_suffix

#uncorrected
fascicle_anova_p <- sapply(fascicle_anova, function(v) v$"Pr(>F)"[1])
fascicle_anova_p05_unc <- as.data.frame(fascicle_anova_p[fascicle_anova_p < 0.05])
print(fascicle_anova_p05_unc) 
```
#### Parametric anxiety net fascicles
```{r indiv_fascicle_anxiety_net_anxiety_dose}

@@

#### Parametric nonanxiety net fascicles
```{r nonanxiety_net_anxiety_dose}

>>>>

    anxietyGrouping_mean_UF_by_sex_gam <- gam(mean_UF_vol ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = F), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
  summary(anxietyGrouping_mean_UF_by_sex_gam)

@@

#anova
fascicle_lm_anova <- lapply(fascicle_lm, anova)

#uncorrected
fascicle_anova_lm_p <- sapply(fascicle_lm_anova, function(v) v$"Pr(>F)"[1])
fascicle_anova_lm_p05_unc <- as.data.frame(fascicle_anova_lm_p[fascicle_anova_lm_p < 0.05])
print(fascicle_anova_lm_p05_unc)

#fdr corrected
fascicle_anova_lm_fdr <- fdr_anova_generic(fascicle_lm_anova, 1, print_unc_df = TRUE)
print(fascicle_anova_lm_fdr)

#gam
fascicle_gam <- lapply(fascicle_names_w_prop_suffix, function(x) 
{
  gam(substitute(i ~ anxiousAndMeds_or_healthy + +osex+ s(PAT_AGE_AT_EXAM, k=4, fx=F), list(i = as.name(x))), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
})
names(fascicle_gam) <- fascicle_names_w_prop_suffix

#anova
fascicle_anova_gam <- lapply(fascicle_gam, anova)

#uncorrected
fascicle_anova_gam_p <- sapply(fascicle_anova_gam, function(v) v$p.pv[2])
print(as.data.frame(fascicle_anova_gam_p))
fascicle_anova_gam_p05_unc <- as.data.frame(fascicle_anova_gam_p[fascicle_anova_gam_p < 0.05])
print(fascicle_anova_gam_p05_unc)

#fdr corrected
fascicle_anova_gam_fdr <- round(p.adjust(fascicle_anova_gam_p, method = "fdr"),3)
fascicle_anova_gam_fdr_p05 <- as.data.frame(fascicle_anova_gam_fdr[fascicle_anova_gam_fdr < 0.05])
print(fascicle_anova_gam_fdr_p05) 
```

@@

### 3 meet FDR - C_FPH_R_prop	0.037			C_FP_R_prop	0.042			DRTT_R_prop	0.042
df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
  filter(anxiety_dose != -1) %>%
  mutate(anxiety_dose_factor = ordered(anxiety_dose))

#lm
fascicle_lm <- lapply(fascicle_names_w_prop_suffix, function(x) 
{
  lm(substitute(i ~ anxiety_dose + PAT_AGE_AT_EXAM, list(i = as.name(x))), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
})
names(fascicle_lm) <- fascicle_names_w_prop_suffix

#anova
fascicle_anova_lm <- lapply(fascicle_lm, anova)

#fdr corrected
fascicle_anova_lm_fdr <- fdr_anova_generic(fascicle_lm_anova, 1, print_unc_df = TRUE)
print(fascicle_anova_lm_fdr)

#uncorrected
fascicle_anova_lm_p <- sapply(fascicle_anova_lm, function(v) v$"Pr(>F)"[1])
fascicle_anova_lm_p05_unc <- as.data.frame(fascicle_anova_lm_p[fascicle_anova_lm_p < 0.05])
print(fascicle_anova_lm_p05_unc)

#gam
fascicle_gam <- lapply(fascicle_names_w_prop_suffix, function(x) 
{
  print(x)
  gam(substitute(i ~ anxiety_dose + osex+s(PAT_AGE_AT_EXAM, k=4, fx=F), list(i = as.name(x))), data = df_demo_and_fascicles_no_unclass_anxiety_dose)
})
names(fascicle_gam) <- fascicle_names_w_prop_suffix

#anova
fascicle_anova_gam <- lapply(fascicle_gam, anova)

#uncorrected
fascicle_anova_gam_p <- sapply(fascicle_anova_gam, function(v) v$p.pv[2])
print(as.data.frame(fascicle_anova_gam_p))
fascicle_anova_gam_p05_unc <- as.data.frame(fascicle_anova_gam_p[fascicle_anova_gam_p < 0.05])
print(fascicle_anova_gam_p05_unc)

#fdr corrected
fascicle_anova_gam_fdr <- round(p.adjust(fascicle_anova_gam_p, method = "fdr"),3)
fascicle_anova_gam_fdr_p05 <- as.data.frame(fascicle_anova_gam_fdr[fascicle_anova_gam_fdr < 0.05])
print(fascicle_anova_gam_fdr_p05) 
```
#### Parametric anxiety net fascicles -> needs GAM
```{r indiv_fascicle_anxiety_net_anxiety_dose}

@@

#### Parametric nonanxiety net fascicles --> Needs gam
```{r nonanxiety_net_anxiety_dose}
